From Freebase to Wikidata: The Great Migration

### 2015-10-09 paper.tex
Fix some TODOs and reply of other
I am not sure if I have really addressed your TODOs

Wikidata\footnote{Wikidata: \url{https://www.wikidata.org/wiki/Wikidata:Main_Page}}
is a~collaborative knowledge base
launched in October 2012 and hosted by the Wikimedia Foundation.
Its community has been growing quickly since the beginning, and as of mid 2015,
the community comprises about 6,000 active contributors.

@@

\subsection{Data Quality}

@@

The last challenge concerns the data mappings between Freebase topics and properties
and Wikidata items and properties.
Two mappings between Freebase topics and Wikidata items were initially available,
and in addition to those, we worked on further mappings.
A~first one has been created by Google in October 2013%
\footnote{Freebase mappings: \url{http://developers.google.com/freebase/data}}
and is based on Wikipedia links already present in Freebase: if a~Freebase topic and
a~Wikidata item share at least two Wikipedia links, they are assumed to describe the same subject.
The quality of this mapping is considered very good by the Wikidata community,
who thus have uploaded it to the Wiki and further curated and maintained it by hand.
It maps 1.15M~Freebase topics to their corresponding Wikidata items.
A~second actively maintained mapping has been created by Samsung.%
\footnote{Samsung mappings: \url{http://github.com/Samsung/KnowledgeSharingPlatform}}
It is based on the same idea, but matches a~Freebase topic with a~Wikidata item
even if there is only a~single shared Wikipedia link.
The precision of the mapping is naturally lower compared to Google's mapping,
as there are more wrong matches (often because there is no clear separation between topics
and disambiguation pages in Wikipedia), however, the recall increases to 4.4M~links.
As we have seen before \todo{Where?}, our quality target is not very high \todo{We should never write this},
so we have chosen to merge the two dumps \todo{The mappings dumps I suppose?} and, for the resulting 6,000 conflicts,
decided to prioritize the mapping given by Wikidata \todo{That is, Google's?}.
To improve the resulting mapping, we have also tried to do some reconciliation
based on external database IDs shared by Freebase and Wikidata, like MusicBrainz \todo{Citation needed}, VIAF \todo{Citation needed}, \emph{etc.}
With this technique, we were able to match 800K~IDs \todo{IDs? Is that MusicBrainz or VIAF IDs?},
creating a~mapping for 600K~topics---most of them already in our dataset \todo{Which dataset?}.
This resulted in an additional 84K items mapped.
We also used data \todo{What data exactly?} from Google's Knowledge Graph \todo{Citation desirable} to add 100K~further mappings
by also matching a~topic and an item if they share a~Wikipedia link \todo{Wasn't it leveraging the Knowledge Graph?}.
There is some potential to add some more data by looking at functional relations
like ``father'' and ``mother'', but these relations only apply to relatively small sets of data
(like well known families) and the functional assumptions may run into some edge cases.
For example, the \texttt{/people/person/parents} property in Freebase also covers stepparents,
which may create cases where a~person has more than one male or female \texttt{/people/person/parents}.
Eventually, with these four sources \todo{Google, Samsung, MusicBrainz, VIAF, Knowledge Graph. 5 Sources?}, we mapped 4.56M~items.
To the best of our knowledge, therewith we have already mapped
most of the topics that could be mapped automatically, 
which is also backed by the comparably small increases gained from the ID reconciliation approach \todo{Referring to MusicBrainz and VIAF?}
and the Knowledge Graph data.
Furthermore, the mapped topics have an average number of facts of about~13.9,
whereas the topics that were not mapped have an average number of 5.7~facts.
We have mapped the majority of topics with more than 80~facts.
This allows us to conclude that we have mapped the most important items of Freebase \todo{Easy "reviewer 2" question: why 80?}.

>>>>

Wikidata\footnote{Wikidata: \url{https://www.wikidata.org}}
is a~collaborative knowledge base
launched in October 2012 and hosted by the Wikimedia Foundation.
Its community has been growing quickly since the beginning, and as of mid 2015,
the community comprises about 6,000 active contributors.

@@

\subsection{Data Quality}
\label{sec-dataquality}

@@

The last challenge concerns the data mappings between Freebase topics and properties
and Wikidata items and properties.
Two mappings between Freebase topics and Wikidata items were initially available,
and in addition to those, we worked on further mappings.
A~first one has been created by Google in October 2013%
\footnote{Freebase mappings: \url{http://developers.google.com/freebase/data}}
and is based on Wikipedia links already present in Freebase: if a~Freebase topic and
a~Wikidata item share at least two Wikipedia links, they are assumed to describe the same subject.
The quality of this mapping is considered very good by the Wikidata community,
who thus have uploaded it to the Wiki and further curated and maintained it by hand.
It maps 1.15M~Freebase topics to their corresponding Wikidata items.
A~second actively maintained mapping has been created by Samsung.%
\footnote{Samsung mappings: \url{http://github.com/Samsung/KnowledgeSharingPlatform}}
It is based on the same idea, but matches a~Freebase topic with a~Wikidata item
even if there is only a~single shared Wikipedia link.
The precision of the mapping is naturally lower compared to Google's mapping,
as there are more wrong matches (often because there is no clear separation between topics
and disambiguation pages in Wikipedia), however, the recall increases to 4.4M~links.
As we have seen in section \autoref{sec-dataquality} the mapped data will be human curated before the importation,
so we have chosen to merge the two mapping dumps and, for the resulting 6,000 conflicts,
decided to prioritize the Google's mapping.
To improve the resulting mapping, we have also tried to do some reconciliation
based on external databases IDs shared by Freebase and Wikidata, like
MusicBrainz,\footnote{MusicBrainz: \url{https://musicbrainz.org}}
VIAF,\footnote{VIAF: \url{http://viaf.org}} \emph{etc.}
With this technique, we were able to match 800K~external database IDs \todo{not sure if it's understandable},
creating a~mapping for 600K~topics---most of them already in the merge of Google's and Samsung's mappings.
This resulted in an additional 84K items mapped.
We also used Google's Knowledge Graph\footnote{Google Knowledge Graph introduction blog post: \url{https://googleblog.blogspot.com/2012/05/introducing-knowledge-graph-things-not.html} \todo{Better reference?}} to add 100K~further mappings
by also matching a~topic and an item if they share a~Wikipedia link \todo{Wasn't it leveraging the Knowledge Graph? -- Yes, but not sure how to rewrite this section. I have added a reference to the introduction article. We should maybe have Denny's input about it}.
There is some potential to add some more data by looking at functional relations
like ``father'' and ``mother'', but these relations only apply to relatively small sets of data
(like well known families) and the functional assumptions may run into some edge cases.
For example, the \texttt{/people/person/parents} property in Freebase also covers stepparents,
which may create cases where a~person has more than one male or female \texttt{/people/person/parents}.
Eventually, with these four sources \todo{Google, Samsung, MusicBrainz, VIAF, Knowledge Graph. 5 Sources? -- Google, Samsung, external IDs, Knowledge Graph}, we mapped 4.56M~items.
To the best of our knowledge, therewith we have already mapped
most of the topics that could be mapped automatically, 
which is also backed by the comparably small increases gained from the ID reconciliation approach \todo{Referring to MusicBrainz and VIAF? -- yes}
and the Knowledge Graph data.
Furthermore, the mapped topics have an average number of facts of about~13.9,
whereas the topics that were not mapped have an average number of 5.7~facts.
We have mapped the majority of topics with more than 47~facts (191K~non mapped topics \textit{vs.} 195K~mapped).
This allows us to conclude that we have mapped the most important items of Freebase.
